Location Classification on Tweets

### 2016-03-10 docs/paper.tex
i i did intro

Twitter is an online platform that lets users to share posts with their followers, limited with at most 140 characters, called as tweets. Tweets can be almost anything that we share on internet; a personal message stating our views, a link to an article, a picture and etc.. There are no boundaries except the character limit. In 2009, Twitter introduced an option to include geographic location(geolocation) information on tweets\footnote{\url{https://blog.twitter.com/2009/location-location-location}}. Since then, a lot of twitter users have been sharing their geolocation with their tweets(or geotagging their tweets). Depending on the context of the tweet, having the geolocation may be very valuable. For example a tweet about a Pizza franchise or a political campaign, if geotagged, may point to an improvement with exact location or contribute to the statistics of a specific area. Unfortunately, geolocation of a tweet is not shared by default or in other words, most of the tweets are not geotagged, unless explicitly specified. Inferring the geolocation of a tweet is what this paper is about.

To be able to infer this information, we can try to use linguistic habits shared by the people who are within the same location. As humans, our spatial cognition deals with updating and managing the knowledge about our environment. Spatial cognition changes when we move between environments, but as we stay within the boundaries of a high level environment(i.e. state, city, borough), there may be some high-level constants that doesn't change. If some of these constants are shared commonly between people, it may lead them to have similar linguistic habits, in this case, textual features in their tweets. If we group the geotagged tweets sent within a high-level location, it may be possible to extract these features, if they exist.

@@

Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people within the same location? If there are, can they help us determine if a tweet is sent within that high-level location?"

>>>>

Twitter is an online platform that lets users share posts with their followers, limited to at most 140 characters, called tweets. Tweets can be almost anything that we share on the internet, for example: a personal message stating our views, a link to an article or a picture. There are no boundaries except the character limit. In 2009, Twitter introduced an option to include geographic location (geolocation) information with tweets\footnote{\url{https://blog.twitter.com/2009/location-location-location}}. Since then, a lot of twitter users have been sharing their geolocation with their tweets (or geotagging their tweets). Depending on the context of the tweet, having the geolocation may be very valuable. For example a tweet about a Pizza franchise or a political campaign, if geotagged, may point to an improvement with exact location or contribute to the statistics of a specific area. Unfortunately, geolocation of a tweet is not shared by default. In other words, most of the tweets are not geotagged, unless explicitly specified. Inferring the geolocation of a tweet is what this paper is about.

To be able to infer this information, we can try to use linguistic habits shared by the people who are in the same location. As humans, our spatial cognition deals with updating and managing the knowledge about our environment. Spatial cognition changes when we move between environments, but as we stay within the boundaries of a high-level environment(i.e. state, city, borough), there may be some high-level constants that doesn't change. If some of these constants are shared commonly between people, it may lead them to have similar linguistic habits, in this case, textual features in their tweets. If we group the geotagged tweets sent within a high-level location, it may be possible to extract these features, if they exist.

@@

Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people in the same location? And if there are, can they help us determine if a tweet is sent within that high-level location?"
